\documentclass{article}
\usepackage[english]{babel}
\usepackage{enumerate, latexsym, amssymb, amsmath}
\usepackage{framed, multicol}
\newenvironment{forthel}{\begin{leftbar}}{\end{leftbar}}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\tmaffiliation}[1]{\\ #1}
\newcommand{\tmem}[1]{{\em #1\/}}
\newenvironment{enumeratenumeric}{\begin{enumerate}[1.] }{\end{enumerate}}
\newenvironment{proof}{\noindent\textbf{Proof\ }}{\hspace*{\fill}$\Box$\medskip}
\newenvironment{quoteenv}{\begin{quote} }{\end{quote}}
\newtheorem{axiom}{Axiom}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{signature}{Signature}
\newtheorem{proposition}{Proposition}
%%%%%%%%%% End TeXmacs macros

\newcommand{\event}{UITP 2018}
\newcommand{\dom}{Dom}
\newcommand{\fun}{aFunction}
\newcommand{\sym}{sym}
\newcommand{\halfline}{{\vspace{3pt}}}
\newcommand{\tab}{{\hspace{1cm}}}
\newcommand{\ball}[2]{B_{#1}(#2)}
\newcommand{\llbracket}{[}
\newcommand{\rrbracket}{]}
\newcommand{\less}[1]{<_{#1}}
\newcommand{\greater}[1]{>_{#1}}
\newcommand{\leeq}[1]{{\leq}_{#1}}
\newcommand{\supr}[1]{\mathrm{sup}_{#1}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}

\begin{document}

\title{An SAD3 Formalization of the Basic Number Systems for Walter Rudin's
\it{Principles of Mathematical Analysis}}

\author{Roman Pl}

\date{August 25, 2018}

\maketitle


\section{Einleitung}
SAD3 kann formalieserte Texte verifizieren, die für Menschen angenehm lesbar sind.
Dies wird in diesem Text dargestellt. Es folgen die Kapitel von Ordered Set, Field, Ordered Field von {\it Principles of Mathematical Analysis} by Walter Rudin \cite{Rudin}.\\
Die Kapitel Reel Field and Complex Field sind in seperaten Texten.\\

Die Datein ord-set.ftl, field.ftl, ord-field.ftl und complex.ftl sind nah am Rudin geschrieben. Für die Abgabe und zusammenführung mit den anderen Arbeitgruppen wurden die Dateien in den spezialen Fall von reellen Zahlen umgeschrieben. Praktisch gesehen war das Umschreiben nicht viel, aber das Wiederherstellen der Funktionalität war mühsam, da es durch den erhöhten Kontext (4 Kapitel) in manchen Beweisen zu Problemen kommt.\\
Lösung dafür ist, die Beweise mit Attributen zu ergänzen z.B. "(by Satz-name)".
Ich möchte mit der Anmerkung "wenig Umschreiben" unterstreichen, wie gut die Modularität von SAD3 funktioniert.\\

Die ForThel-Dateien existieren für fast jedes Kapitel in zwei Versionen.\\
Die zwei Versionen unterscheiden sich insofern, dass z.B. in OrdSet.ftl die Relationen mit R benannt sind und die Relation deshalb beliebig ist. Das heißt, dass man beweisen kann, dass, falls man ein 2-stelliges Funktionssymbol hat, dieses eine Relation ist, falls es eine ist.\\
In der Version in Master.ftl ist OrdSet in der Schreibweise mit < geschrieben, sodass spätere Kapitel dies benutzen können.\\

Am dramatischsten ist der Unterschied in Field.ftl zu sehen, da mul(AM)[( - , - )] zu einem einfachen * geworden ist.\\


\subsection{Megentheorie}

Formalisierung von Rudins Ordered Set-Kapitel und grundlegende Mengentheorie, Begriffe.\\

\begin{forthel}
[set/-s] [element/-s] [belong/-s] [subset/-s] [relation/-s] [number/-s]

\begin{signature} A real number is a notion.

\end{signature}
\begin{definition} $\mathbb{R}$ is the set of real numbers. 

\end{definition}
\begin{axiom} every real numbers is element of $\mathbb{R}$.

\end{axiom}


Let S,T,A,B,C denote sets.

\begin{definition} DefSubset.   A subset of S is a set T

\end{definition}
such that every element of T is a element of S.

\begin{definition} DefEmpty.    S is empty iff S has no elements.

\end{definition}

\begin{signature} A relation is a notion.

\end{signature}

\begin{signature} An order is a relation.

\end{signature}

\begin{signature}Let $<$ be a relation.

\end{signature}

\begin{signature} Let x,y be elements of $\mathbb{R}$. x$<$y is an atom.

\end{signature}

Let x,y,z denote real numbers.

\begin{axiom} x$<$y or y$<$x or x = y.

\end{axiom}

\begin{axiom} Then not ((x$<$y and y$<$x) or (x$<$y and y=x) or (x=y and y$<$x)).

\end{axiom}
\begin{axiom} If x$<$y and y$<$z then x$<$z.

\end{axiom}



\begin{definition} upperBound.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
An upper bound of A is an element b of $\mathbb{R}$ such that ( y$<$b or y = b ) for every element y of A.

\begin{definition} lowerBound.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
A lower bound of A is an element b of $\mathbb{R}$ such that ( b$<$y or y = b ) for every element y of A.

\begin{definition} Supremum.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
Let s be an element of $\mathbb{R}$.
s is supremum of A  iff s is an upper bound of A 
and for every element x of $\mathbb{R}$ if x$<$s then x is not an upper bound of A .

\begin{definition} Infimum.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
Let s be an element of $\mathbb{R}$.
s is infimum of A  iff s is an lower bound of A 
and for every element x of $\mathbb{R}$ if s$<$x then x is not an lower bound of A .

\begin{definition} BoundedBelow.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
A is bounded below  iff 
there exists an element b of $\mathbb{R}$ such that b is a lower bound of A .

\begin{definition} BoundedAbove.

\end{definition}
Assume A is a subset of $\mathbb{R}$.
A is bounded above  iff 
there exists an element b of $\mathbb{R}$ such that b is an upper bound of A .

\begin{definition} leastupperboundproperty.

\end{definition}
Assume R is a subset of $\mathbb{R}$.
R is lub iff for every subset A of R
if (A is bounded above and not empty) then (there exists an element s of R such that s is supremum of A ).

\begin{theorem}
.
\end{theorem}
Assume $\mathbb{R}$ is lub.
Assume B is a subset of $\mathbb{R}$ and not empty and bounded below.
Let L = {a in $\mathbb{R}$ | a is lower bound of B}.
Then there exists an element a of $\mathbb{R}$ such that a is supremum of L and a is infimum of B .

\begin{proof}
L is not empty.
Every element x of B is an upper bound of L.
Then L is bounded above.
Take an element a of $\mathbb{R}$ such that a is supremum of L.
a is an element of L.
\end{proof}





\end{forthel}

\subsection{The Field}

Im Kapitel Field und ord-field werden aus den Axiomen viele einfache Aussagen der Körpertheorie gezeigt und Umformung-, Rechen- und Kürzungsregen gezeigt. Diese sind essenziell für das Weiterrechnen in anderen Beweisen.
Manche Aussagen sind so einfach und der Kontext ist noch so klein, dass SAD diese Aussagen selbstst\"andig beweisen kann.

\begin{forthel}

\begin{signature} A field is a notion.

\end{signature}

Let x,y,z denote real numbers.

\begin{signature} Add. x + y is real number.

\end{signature}
\begin{axiom} A1. Let x, y be real numbers. Then x + y is a real number.

\end{axiom}
\begin{axiom} A2. x + y = y + x.

\end{axiom}
\begin{axiom} A3. (x + y) + z = x + (y + z). 

\end{axiom}
\begin{signature} A4. 0 is element of $\mathbb{R}$ such that for every real number x x + 0 = x.

\end{signature}
\begin{signature} A5. -x is element of $\mathbb{R}$ such that x+(-x) = 0.

\end{signature}

\begin{signature} M1. x * y is a real number.

\end{signature}
\begin{axiom} M2. x * y = y * x.

\end{axiom}
\begin{axiom} M3. (x * y) * z = x * (y * z).

\end{axiom}
\begin{signature} M4. 1 is element of $\mathbb{R}$ such that for every real number x x * 1 = x.

\end{signature}
\begin{axiom} M42. 0 is not equal to 1.

\end{axiom}
\begin{signature} M5. Assume not x = 0. inv(x) is a real number such that inv(x)*x = 1.

\end{signature}

\begin{axiom} D. x*(y + z) = (x*y) + (x*z).

\end{axiom}



\begin{theorem}
 P114a.
If x + y = x + z then y = z.\end{theorem}
\begin{proof}


Assume x + y = x + z.
y  = 0 + y
= ((-x)+x) + y
= -x + (x+y)
= -x + (x+z)
= ((-x)+x) + z
= 0 + z
= z.
\end{proof}


\begin{theorem}
 P114b.
If x + y = x then y = 0.
\end{theorem}
\begin{theorem}
 P114c. 
If x + y = 0 then y = -x.\end{theorem}
\begin{proof}

Assume x + y = 0.
Take z = -x. Then x + z = 0.
Then x + z = x + y. Then y = -x (by P114a).
\end{proof}

\begin{theorem}
 P114d. 
Let x be elements of $\mathbb{R}$. -(-x) = x.
\end{theorem}
\begin{proof}

Then (-x)+x = 0.
Then -(-x) = x (by P114c).
\end{proof}



\begin{theorem}
 P115a.
Let x,y,z be elements of $\mathbb{R}$. If x is not equal to 0 and x*y = x*z then y = z.\end{theorem}
\begin{theorem}
Let x,y be elements of $\mathbb{R}$. If x is not equal to 0 and x*y = x then y = 1.\end{theorem}
\begin{theorem}

Let x,y be elements of $\mathbb{R}$. If x is not equal to 0 and x*y = 1 then y = inv(x).\end{theorem}
\begin{theorem}

Let x be elements of $\mathbb{R}$. If x is not equal to 0 then inv(inv(x)) = x.\end{theorem}



\begin{theorem}
 P116a.
Let x be elements of $\mathbb{R}$. 0*x = 0.\end{theorem}
\begin{proof}

Then (0*x) + (0*x)
= (0+0)*x
= 0*x.
Then 0*x = 0 (by P114b).
\end{proof}

\begin{theorem}
 P116b. 
If x is not equal to 0 and y is not equal to 0 then x*y is not equal to 0.\end{theorem}
\begin{proof}


Let x is not equal to 0 and y is not equal to 0.
Assume the contrary.

Then 1 = (inv(x)*inv(y))*(x*y)
= (inv(x)*inv(y))*0
= 0 .
Contradiction.
\end{proof}


\begin{lemma} L1.


(-x)*y = -(x*y).\end{lemma}
\begin{proof}


((-x)*y) + (x*y) .= (y*(-x)) + (y*x) (by M2)
.= y*(-x+x) (by D) 
.= (-x+x)*y (by M2)
.= 0*y (by A2, A5)
.= 0 (by P116a, M2).

\end{proof}
 
\begin{theorem}
 P116c.
(-x)*y = -(x*y) = x*(-y).\end{theorem}
\begin{proof}

Then(-x)*y = -(x*y) (by L1).

Then -(x*y) = -(y*x) = (-y)*x = x*(-y).

\end{proof}
 

\begin{theorem}
 P116d.
(-x)*(-y)= x*y.\end{theorem}


Let x - y stand for x + (-y).


Let x $>$ y stand for y $<$ x.
Let x $\leq$ y stand for x$<$y or x=y.
Let x $\geq$ y stand for y $\leq$ x.



\end{forthel}

\subsection{The Ordered Real Field}
Im Kapitel Orderen Field werden sowohl Aussagen von Ordered Set als auch von Field benutzt, um Aussagen über Ordered Field zu zeigen.
Aber zuerst müssen Axiom A1 und Axiom A2 einführt werden.
In diesem Kapitel muss man zusätzlich bestimmte Aussagen für SAD betonen, da der Kontext schon ziemlich groß ist.

\begin{forthel}
	\begin{axiom} A1. If y$<$z then x+y$<$x+z.

\end{axiom}
	\begin{axiom} A2. If x$>$0 and y$>$0 then x*y$>$0.

\end{axiom}
	
	\begin{theorem}
 P118a. If x$>$0 then -x$<$0. 
\end{theorem}	\begin{proof}

	Assume x$>$0. Then 0= -x + x $>$ -x + 0.
	Then -x$<$0.
	\end{proof}

	\begin{theorem}
 P118a2. If x$<$0 then -x$>$0. 
\end{theorem}	\begin{proof}

	Assume x$<$0. Then 0= -x + x $<$ -x + 0.
	Then -x$>$0.
	\end{proof}

	\begin{theorem}
 P118b. If x$>$0 and y$<$z then x*y$<$x*z.
\end{theorem}	\begin{proof}

	Assume x$>$0 and y$<$z. 
	Let us show that z-y $>$ y-y = 0.
	y$<$z.
	then (-y)+y$<$(-y)+z (by A1).
	
	end.
	Then x*(z-y)$>$0.
	Then x*z = (x*(z-y))+(x*y).
	
	Take a = x*(z-y) and b = x*y.
	Then a$>$0.
	Then x*z = a + b $>$ 0+b = (x*y).
	
	Then x*z $>$ x*y.
	\end{proof}

	\begin{theorem}
 P118c. If x$<$0 and y$<$z then x*y$>$x*z.
\end{theorem}	\begin{proof}

	Assume x$<$0 and y$<$z.
	Then -x$>$0 (by P118a2).
	Then z-y$>$0. 
	Let us show that z-y$>$0.
	y$<$z.
	then (-y)+y$<$(-y)+z (by A1).
	then z-y$>$y-y=0.
	end.
	Then -(x*(z-y)) = (-x)*(z-y) (by P116c).
	Then (-x)*(z-y) $>$ 0.
	Then x*(z-y) $<$ 0.
	Then (x*z) - (x*y) $<$ 0.
	
	Take a = (x*z) and b = - (x*y).
	Then a+b$<$0.
	Then a $<$ -b.
	
	Then x*z $<$ x*y.
	\end{proof}

	
	\begin{theorem}
 P118d. If not x = 0 then x*x $>$ 0.
\end{theorem}	\begin{proof}

	Case x$>$0. Then x*x $>$ 0.
	end.
	Case x$<$0. Then -x$>$0. Then x*x = (-x)*(-x)$>$0.
	end.
	
	\end{proof}

	\begin{lemma} 1$>$0. 

\end{lemma}
	\begin{proof}

	Then 1 = 1*1 $>$ 0 (by P118d, M42).
	\end{proof}

	
	\begin{theorem}
 P118e1. If 0$<$y then 0 $<$ inv(y).
\end{theorem}	\begin{proof}

	(1) Assume the contrary.
	Then y*inv(y) $\leq$ 0.
	Then y*inv(y) = 1 $>$ 0.
	Contradiction.
	
	\end{proof}

	\begin{theorem}
 P118e2. If 0$<$x$<$y then 0 $<$ inv(y)$<$inv(x).
\end{theorem}	\begin{proof}
 
	Assume 0$<$x$<$y.Then 0$<$inv(y) and 0$<$inv(x).
	Then inv(x)*inv(y)$>$0.
	Take a = inv(y)*inv(x).	
	Then x$<$y. Then x*a$<$y*a.
	Then x*(inv(x)*inv(y))$<$ y*(inv(x)*inv(y)).
	Then (x*inv(x))*inv(y)$<$ (y*inv(y))*inv(x).
	Then inv(y) $<$ inv(x).
	
	\end{proof}

	

\end{forthel}








\subsection{Zusätzliche Aussagen als Vorbereitung}
In diesem Kapitel werden Aussagen gezeigt, die für die Kapitel Reals-A und Reals-B wichtig sind.
Es war nicht möglich eine weitere Datei an Master.ftl anzuhägen, da der Kontext zu groß war
un da SAD schwierige Existenzaussagen zeigen muss, die zeitaufwendig sind. Besonders schwierig war der Beweis P118b. Diesem ist die Datei Reals-B gewidmet.
 
\begin{forthel}
	\begin{signature} A natural number is a real number.

\end{signature}
	
	\begin{definition} NatSet.

\end{definition}
	$\mathbb{N}$ is the set of natural numbers.
	
	\begin{axiom} 0 is natural number.

\end{axiom}
	Let n, m denote a natural number.
	\begin{axiom} n+1 is a natural number.

\end{axiom}
	\begin{axiom} n $\geq$0.

\end{axiom}
	
	\begin{signature} a natural number is a real number.

\end{signature}
	
	

	
	\begin{theorem}
 Lis2. Let n be a natural number and not n=0. If n*x$<$m then x$<$m*inv(n).
\end{theorem}	\begin{proof}

	Assume n*x$<$m.
	n $>$ 0.
	inv(n) $>$ 0 (by P118e1).
	inv(n)*(n*x)$<$inv(n)*m (by P118b).
	(x*n)*inv(n)$<$m*inv(n).
	x*(n*inv(n))$<$m*inv(n).
	x*1$<$m*inv(n).
	x$<$m*inv(n).
	\end{proof}

	\begin{theorem}
 Lis3. Let n be a natural number and not n=0. if m$<$n*y then m*inv(n)$<$y.
\end{theorem}	\begin{proof}

	Assume m$<$n*y.
	n $>$ 0.
	inv(n) $>$ 0 (by P118e1).
	inv(n)*m$<$inv(n)*(n*y) (by P118b).
	m*inv(n)$<$(n*inv(n))*y.
	m*inv(n)$<$1*y.
	m*inv(n)$<$y.
	\end{proof}

\end{forthel}

\subsection{Archimedian properties}
Finally we have formalized what Rudin assumes for the proof of his 1.20. We can now contrast the formalization with Rudin's original.

\newpage
The next two theorems correspond to Theorems 1.20(a) and (b) of Rudin. We start with the original introductory text of Rudin and then display the two texts in parallel to illustrate the closeness of the formalization to the original.

\vspace{1cm}

The next theorem could be extracted from this construction [of the real numbers] with very little extra effort. However, we prefer to derive it from Theorem 1.19 since this provides a good illustration of what one can do with the least-upper-bound property.


\newpage


\section{Bemerkungen}







\begin{thebibliography}{1}

\bibitem{Rudin}
  Walter Rudin,
  \textit{Principles of mathematical analysis},
  McGraw-Hill,
  1976.

\end{thebibliography}
  


\end{document}
